### 2018-03-16 Paper/jaccardbaetica.tex
add new lines in conclusion

No strong relation between stamps and spatial distance have been detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only few similar stamps between closer amphora workshops were found. In any case, our results show that most similar amphoric stamps were detected in closer workshops and not in other areas. These stamps tend to share the same area of production but there is not relation of similarity in general.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are similar stamps in closer workshops. Rather the stamps detected in closer amphorae workshops seem not move from other farthest workshops. Additionally they could have been "wrongly" catalogued twice in different mode in spite of belonging to the same place or being closer between each other. 
%los que aparecen cerca son porque están cerca o puede haber confusion entre talleres

By contrast, we have located different stamps in a same amphora workshop. Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Probably our results could be interpreted due to several reason according to previous hypotheses. The use of these amphoric stamps could be exclusively running by the owner or family to distinguish the amphora workshop (CITAR).

@@

As summary, this method presented here provides a potential tool to understand mechanisms of production based on the similarity of artefacts.  This method have identified

highlight

>>>>

No strong relation between stamps and spatial distance have been detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only similar stamps between closer amphora workshops were found. In any case, our results show that most similar amphoric stamps were detected in closer workshops and not in other areas. These stamps tend to share the same area of production but there is not a general relation between groups of amphora workshops and area.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are similar stamps in closer workshops. Rather the stamps detected in closer amphorae workshops seem not move from other farthest workshops. Additionally they could have been catalogued with different names by authors (METER PONSICH Y DRESSEL) in spite of belonging to the same place or being closer between each other. We also identify different stamps in other closer workshops. 
%los que aparecen cerca son porque están cerca o puede haber confusion entre talleres

By contrast, we have located different stamps in a same amphora workshop. Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Probably our results could be interpreted due to several reason according to previous hypotheses. The use of these amphoric stamps could be exclusively running by the owner or families to distinguish the amphora workshop (CITAR).

@@

As summary, this method presented here provides a potential tool to understand mechanisms of production based on the similarity of artefacts. This method have identified differences in the case of the amphoric production within Roman Empire. Accordingly the results have highlighted to interpreter the complex economical processes based on  the archaeological evidence.
